\documentclass{article}
\usepackage{courier}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{titlesec}
\usepackage{hyperref}

\newcommand{\sectionbreak}{\clearpage}

\date{}

\begin{document}

\title{
  \huge{Bylaws of the IEEE Student Branch}\\
  \Large{California Polytechnic State University}
}
\maketitle
\thispagestyle{empty}

\pagenumbering{roman}

\tableofcontents
\clearpage

\pagenumbering{arabic}

\section{Officers}

\begin{enumerate}
\item The club shall consist only of members of the IEEE national organization.
\item The club shall consist of the following officers
  \begin{itemize}
    \item Branch President
    \item Internal Vice President
    \item External Vice President
    \item Treasurer
    \item Secretary
    \item Webmaster
    \item Publicity Manager
    \item Parts Manager 
    \item Assistant Parts Manager
    \item Projects Manager
    \item Corporate Relations Manager
    \item Events Coordinator
  \end{itemize}
\item No more than two officers may fulfill the role of Events Coordinator. Additionally, no more than two officers may fulfill the role of Corporate Relations Manager. All other positions may be fulfilled by no more than one officer.
\item The first five positions (Branch President, Internal Vice President, External Vice President, Treasurer, and Secretary) shall be denoted as ``executive'' positions. 
\item The Branch President may appoint any IEEE member to the role of Parts Manager or Assistant Parts Manager. All other positions must be obtained by means of an election. The election process is detailed in section [ELECTION].
\item If an officer in a ``non-executive'' position leaves the club for any reason during the school year, the Branch President may appoint any IEEE Member to fill the vanancy.
\item If an officer in a ``executive'' position leaves the club for any reason during the school year, then a special election open only to current officers of the club shall be held to fill the vacancy. The special election process is detailed in section [ELECTION], subsection [SPECIAL ELECTION].
\end{enumerate}

\section{Club Management}

\subsection{The Decision Process}
\begin{enumerate}
\item The branch president has the ``final word'' on all club decisions.
\item The branch president may be overridden by the vote of both vice presidents.
\item In ``monetary issues'' the treasurer also has a vote.
\item ``Monetary issues'' are defined to be issues directly related to either purchases for the club, officer reimbursements, or the prices of parts or kits.
\item If applicable, the combined vote of the branch president and the treasurer shall override the veto of both vice presidents.
\end{enumerate}

\subsection{Officer Requirements}
\begin{enumerate}
\item Officers shall attend all assigned ``officer in-charge'' hours each week.
\item Officers shall attend all club meetings.
\item Officers shall any position-speific requirements as defined in his/her ``officer datasheet''.
\end{enumerate}

\subsection{Officer Dismissal}
\begin{enumerate}
\item Unexcused absence from 2 consecutive club meetings is grounds for dismissal.
\item Unexcused absence from 5 or more ``officer in-charge'' hours in one quarter is grounds for dismissal.
\item Officers may be dismissed from the club by a simple majority vote of the current officers.
\item Only the branch president may initialize dismissal proceedings.
\item Dismissal proceedings shall consist of the following:
  \begin{enumerate}
    \item The branch president shall inform the officer privately of the intent to initiate dismissal proceedings
    \item Within one week, a special officer meeting will be convened.
    \item The branch president shall state to the club the justification for dismissal.
    \item The officer shall have the opportunity to present a defense.
    \item The club will then vote by secret ballot.
  \end{enumerate}
\end{enumerate}

\section{Elections}

\subsection{General Elections}
\begin{enumerate}
\item Only members of the IEEE national organization may run for officer positions or vote in general elections.
\item General officer elections shall be held every spring quarter. 
\item Any member may run for no more than two positions.
\item Only a current officer may run for the position of branch president.
\item If no member applies for a position during the application period, the incoming branch president must appoint a member by the beginning of the next fall quarter.
\item Write-ins shall not be recoginized on the club ballot.
\item Voting results shall may be presented live in a predetermined fashion.
\item Ties shall be resolved by a special officer election for the members who tied.
\item The general election shall follow the following timeline:
  \begin{enumerate}
  \item The application period shall begin the second week of spring quarter.
  \item The application period shall end the fourth week of spring quarter.
  \item Voting will start immediately at the conclusion of the application period.
  \item The voting period shall last 48 hours.
  \item If any portion of the voting period overlaps with a non-weekday, then voting shall be extended for the duration of the overlap.
  \item Election results shall be results the fifth week of spring quarter
  \end{enumerate}
\end{enumerate}

\subsection{Special Officer Elections}
\begin{enumerate}
\item Only club officers may vote in a special election.
\item Only club officers, or, as described above, members who tied in a general election, may run in a special election.
\item A special election shall follow the following timeline:
  \begin{enumerate}
  \item The application period shall last 24 hours.
  \item If the candidates are members who tied in a general election, there shall be no application period.
  \item The voting period shall last 24 hours
  \item The voting period will start immediately at the conclusion of the application period.
  \item If any portion of the voting period overlaps with a non-weekday, then voting shall be extended for the duration of the overlap.
  \end{enumerate}
\end{enumerate}

\subsection{Freshman Representatives}
\begin{enumerate}
\item The branch president and both vice presidents shall interview and select ``freshman representatives.''
\item There shall be no more than two freshman representatives.
\item The freshman representative selection process shall follow the same time as the general election, with ``fall'' substituted for ``spring.''
\end{enumerate}

\section{Student Branch Membership Benefits}
\begin{enumerate}
\item Any student shall be considered a member of the club if they are a member of the IEEE national organization.
\item Club members shall receive the following benefits:
  \begin{enumerate}
  \item The opportunity to apply for funding for personal projects. The club shall own any items purchased for the projects, but the student shall have a opportunity to purchase the items back from the club for 10\% of their original purchase price.
  \item Free passive components, defined to be resistors and capacitors. Students will be limited to 10 components per transaction.
  \item Inclusion of their resume in the club resume portfolio.
  \item The opportunity to participate in club industry tours.
  \item A 20\% discount on all parts and kits.
  \end{enumerate}
\end{enumerate}

\section{Parts Sales}
\begin{enumerate}
\item The parts manager shall only stock parts related to kits being offered for EE classes.
\item Refunds may not be offered for any parts or kits sold, unless the item is factory sealed and is unopened.
\item The parts manager has the authority to set all part prices, subject to the approval of the Branch President. This includes removing the club member discount for select parts or kits.
\item The parts manager is not required to attend club meetings or club events beyond those required to fill the normal duties of the position.
\item The parts manager and assistant parts manager shall receive a 50\% discount on all parts and kits sold.
\end{enumerate}

\section{Reimbursements}
\begin{enumerate}
\item Any officer in the club may apply for a reimbursement for purchases made on behalf of the club.
\item The treasurer must approve all reimbursements.
\item The branch president must approve any reimbursement made on behalf of the treasurer.
\item Club reimbursements are subject to the Electrical Engineering department policy for reimbursements.
\item Money may not be dispersed from the cashbox, for any reason, before a purchase is made.
\end{enumerate}

\section{Ratification and Future Changes}
\begin{enumerate}
\item These bylaws shall be considered ``ratified'', and thus in effect for all officers, if they are approved by the ceiling of 2/3 of the current officers.
\item Approval shall consist of signing this document.
\item The current officers shall be defined by the number of entries in the ``Officer Contact Information'' document.
\item Any change of any kind to this document after its ratification must be approved by 2/3 of current officers.
\end{enumerate}

\end{document}

